Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-08 paper/main.tex
bump version string and URL for eventual resubmission release
note support for IPython shells in metadata table

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
\hline
C1 & Current code version &  v0.2.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.0} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments, and
     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

>>>>

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
\hline
C1 & Current code version &  v0.2.4 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.4} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments, and
     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors, IPython shell. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}
